table

### 2025-04-15 table-process.qmd
update Kappa'

data %>%
select(-Description) %>% 
gt() %>% 
cols_label(Icons = "") %>% 
tab_header(title = md("**Data Collection Strategy**"),
subtitle = "For biographical dictionaries and industry catalogue") %>% 
gtsave("assets/data-collection-process.png")

>>>>

data %>%
select(-Description) %>% 
gt() %>% 
cols_label(Icons = "") %>% 
tab_header(title = md("**Data Collection Strategy**"),
subtitle = "For biographical dictionaries") %>% 
gtsave("assets/data-collection-process.png")
